---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# acwri

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

acwri is an academic writing tools package for R users. It integrates various utilities to streamline the academic writing workflow.

## Installation

You can install the development version of acwri from GitHub with:

```{r}
#| eval: false
# install.packages("pak")
pak::pak("jixing475/acwri")
```

## Usage

```{r}
#| include: false
# Reset possible options
options(acwri.description = list())
```

```{r}
#| eval: false
library(acwri)

# More usage examples will be added as the package develops
```

## Code of Conduct

Please note that the acwri project is released with a Contributor Code of Conduct. By contributing to this project, you agree to abide by its terms.
